A Combinatorial Search of Parameterized Quantum Circuit Learning for Chemical Applications

### 2025-01-16 manuscript/main.tex
Thu Jan 16 03:21:02 PM EST 2025

The noisy function fitting dataset is generated by

$f(x) = x + \varepsilon$ such that $\varepsilon \in \mathcal{N} (0, \sigma^{2} )$

@@

For the function fitting dataset, there is only one feature per target value.

For the BSE dataset, various molecular representations are explored, and we settled on using Morgan fingerprints with X parameters. 
For the feature reduction, we use PCA, as explained in Section

\begin{figure}[H]
	\centering	
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../classical_testing/BSE/BSE_16_learning_curve}
		\caption{}
		\label{fig:bse16learningcurve}
	\end{subfigure}
	\hfill
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../classical_testing/BSE/classical_funcfit}
		\caption{}
		\label{fig:classicalfuncfit}
	\end{subfigure}
	\caption{}
	\label{fig:bse16classical}	
\end{figure}

>>>>

The noisy function fitting dataset is generated by
$f(x) = x + \varepsilon$ such that $\varepsilon \in \mathcal{N} (0, \sigma^{2} )$, where $\sigma\approx0.34$. The linear function is $f(x)=x$, quadratic is $f(x) = 0.3967 x^{2} - 3.2807 x + 6.7569$, and sine function is $f(x) = 0.9913 \sin(2.3838 x+0.0344)$. 
The normalized versions are shown in Fig. \ref{fig:train_vs_test}.

@@

The first chemical dataset we explore is the BSE49 dataset. 
This dataset consists of homolytic bond cleavages of X molecules and 49 unique bond types.
One important aspect of this dataset is the choice of molecular representation, or how the molecule is represented in the machine learning models.

For the BSE dataset, various molecular representations are explored, and we settled on using Morgan fingerprints with X parameters. 
80\% train 20\%test Fig. \ref{fig:classicalfuncfit} 
\ref{fig:BSE_classical_features_R2} and \ref{fig:BSE_bse_classical_features_MAE}

For the feature reduction, we use PCA, as explained in Section

\begin{figure}[H]
	\centering	
	\includegraphics[width=\linewidth]{../classical_testing/BSE/classical_funcfit}
	\caption{}
	\label{fig:classicalfuncfit}
\end{figure}
